Coherent optical association of a single molecule

### 2020-10-19 paper.tex
Update on Overleaf.

\begin{abstract}
  We report on coherent association of a single weakly-bound NaCs molecule in an optical tweezer
  through an optical Raman transition without the use of a Feshbach resonance. Our scheme borrows transition dipole moment while reducing photon scattering by selecting a deeply bound electronic excited intermediate state.
  Starting from two atoms in their relative motional ground state,
  we achieve optical transfer efficiency of $69\%$.
  The molecule has a binding energy of $770.200516(24) \mathrm{MHz}$ at $8.8~\mathrm{G}$
  and lifetime up to $1 \mathrm{ms}$ \textcolor{blue}{(1~ms seems long here)} with more than $60\%$ of the molecule created in the
  motional ground state.
  % We demonstrate that coherent creation of a ground-state single molecule is possible, even without Feshbach resonance or narrow optical transition.
  This technique is general without relying on narrow excited state lines or Feshbach resonances and could allow a wider range of molecular species to be assembled atom-by-atom.
\end{abstract}

@@

Diverse species of fully quantum controlled  ultracold molecules are desired for a  wide variety of applications including precision measurements~\cite{Nick_and_Ivan2017, PhysRevA.101.042504} \textcolor{red}{KW: added a citation here for some exotic atomic/molecular species for precision measurements. Can delete this text, if you think it's appropriate, or otherwise remove this reference.}, quantum simulations~\cite{Yao2018}, quantum  information processing~\cite{DeMille2002, Ni2018}, and studies of ultracold chemistry~\cite{Bohn2017,Bala2016,Hu1111}.
While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules below 1~mK~\cite{Norrgard2016, Mitra1366}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020}  have been achieved through the association of ultracold atoms.
% (any place to cite  molecular ion work?)
% cite recent doyle group result on cooling symmetric top molecule? FOR SURE, and other laser cooling works and electro-optical-cooling! Citations are not complete. Add them as you see fit.

Such ultracold molecular association takes advantage of the much developed cooling and trapping techniques for atoms as a starting point. To overcome the challenges of small wavefunction overlap and the large release of binding energy of converting atoms to deeply-bound molecules, a  two-step approach has been established to first associate atom pairs into weakly-bound molecules, and then transfer the molecules from this single internal state to a desired rovibrational and electronic state~\cite{Danzl2008, Ni2008,Lang2008, Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
So far, all of such association processes utilized a magnetic Feshbach scattering resonance and have been applied to bialkali molecules. The only exception is Sr$_2$ where narrow linewidth excited states are available and optical association can be driven coherently~\cite{Reinaudi2012,Stellmer2012}. The requirement of a Feshbach resonance to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited state lines limits the generality of the association technique. % to more diverse species.

Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, schematically shown in Fig.~\ref{f-theory}A, neither using a Feshbach resonance nor a narrow excited state. The resulting single molecule is in a single internal quantum state and predominately in its motional ground state.  Our scheme is based on a choice of vibrational state of the electronic excited state $c^3\Sigma^+(\Omega = 1)$ that has the theoretical best raman Rabi frequency to photon scattering ratio. To further increase this ratio and reduce technical requirements such as intensity stability, we choose an initial and final state where the matrix elements with the excited state are as balanced as possible. This approach minimizes the reliance on system specific properties and could therefore be applied to creating other molecular species or larger molecules atom-by-atom with full quantum state control.
% (also this result represents full quantum-state control of single [neutral] molecules, the second time ever (first being our NaCs Feshbach molecules))

@@

The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}A), where the initial atomic state, the target weakly-bound molecular state are coupled to an excited intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.  %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
The transfer Raman Rabi Rate, $ \Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate which is a sum of all coupling sources %of $\sum_{n=i} \Gamma_e \Omega_i^2 / 4\Delta^2 $,
$\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth~\cite{Wineland2003}. %, depends on both of these matrix elements and the single photon detuning~\cite{Wineland2003}.
Unlike for Raman transitions in atoms, the two matrix elements here, $ \Omega_m$ and $ \Omega_a$, are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
due to the small wavefunction overlap between the atomic state and the excited molecular state, and the scattering is predominantly from the molecular state. Furthermore, the energy difference between the atomic and weakly bound state is small ($ < 1 \mathrm{GHz} $) compared to the single photon detuning, $ \Delta $, so the molecular state can scatter off both beams at roughly the same single photon detuning. Thus, the scattering is given by $ \Gamma_e \Omega_m^2 / 2\Delta^2$ \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi Rate at a fixed total power. Thus, this results in an additional factor of 2 coming from scattering off 2 beams.}.
The ratio between the Raman Rabi frequency and the scattering rate, $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth. To ensure a coherent process, a detuning as large as possible, while maintaining a realistic Raman Rabi frequency, is preferred. %However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
With the multiple excited vibrational states present in a molecular potential, the total scattering rate and Raman Rabi rate become a sum over the scattering rates and Raman Rabi rates of the individual states. %There are also many possible intermediate states to choose from.

Pioneering experiments used weakly bound molecular excited states in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}. However, such choice of state suffers from strong scattering of the nearby atomic excited state to render it incoherent, resulting in molecule loss. This scattering is  proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can  be made smaller by detuning away from the dissociation threshold.

@@

To find the optimal excited intermediate state, we perform a  calculation of the Raman Rabi frequency and scattering rate at different detunings from the atomic threshold taking into account of all states of the $c^3\Sigma^+(\Omega = 1)$ excited molecular state potential (full result in SM)~\cite{Liu2017, Grochola2011}. As shown in Fig.~\ref{f-theory}B, the ratio of the Raman Rabi rate to scattering rate can be made larger for more deeply bound states compared to weakly bound states at a cost of a smaller Raman Rabi frequency.  %Since for a typical molecular potential the spacing between states
% decreases with increasing vibrational levels,
% a weakly bound excited molecular state
% This further increases the scattering rate for a weakly bond excited state.
% Based on these considerations, % a weakly bound excited molecular state may not be the best choice for the intermediate state in the Raman transfer. Thus,
% we calculated both the Raman Rabi frequency and the scattering rate at different detunings (full result is shown in SM). As seen in Fig.~\ref{f-theory}B,
% we found a distinct optimal regime from what has been explored experimentally previously.
% Namely, despite a smaller Raman Rabi frequency at deeply bound intermediate states, the Rabi frequency to scattering rate ratio is much higher as compared to a weakly bound intermediate state.
As a result, we choose a deeply bound molecular excited state ($v'=0$ of $c^3\Sigma^+(\Omega = 1)$) as an intermediate state to drive the Raman transition. %(mention the trend, also v'=12 will work as similarly as v'=0)

@@

As previously discussed, the ratio of the Raman Rabi rate to the scattering rate is proportional to the $ \Omega_a/\Omega_m $ ratio. The smaller this ratio is, the farther the laser needs to be detuned to achieve the same Raman Rabi rate to scattering rate ratio, which lowers the Raman Rabi rate. In addition to reducing how far the laser needs to be detuned from the transition, a larger $ \Omega_a/\Omega_m$ ratio also relaxes the intensity stability requirement, a key potential technical limitation. The position of the two photon resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $ \footnote{There is an additional factor of 2 to account for the Stark shift caused by both beams.}. The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser intensity needs to be stabilized to better than the inverse of this ratio to fluctuate by less than a linewidth in a coherent process. The ratio, $ \Omega_a/\Omega_m $ can be changed through the choice of initial and final states. In particular, it can be made larger by increasing the coupling of the atomic state with the excited molecular state. Due to the small size of the molecular wavefunction, the coupling between the ground atomic state and the excited molecular state is approximately proportional to the value of the relative atomic wavefunction at short distance within the molecular potential. In addition to the confinement, this value is related to the interaction between the two atoms. For states with a large scattering length (positive or negative), the phase shift in the relative wavefunction between the atoms can significantly increase the short range wavefunction (Fig.~\ref{f-theory}C). The increase in the coupling is proportional to (quote/cite Olive's equation?). For our system, we denote the possible hyperfine states of the atoms as $ \ket{\uparrow_{\text{Cs}}} = \ket{F=4,m_F=4}_{\text{Cs}}, \ket{\downarrow_{\text{Cs}}} = \ket{F=3,m_F=3}_{\text{Cs}}, \ket{\uparrow_{\text{Na}}} = \ket{F=2,m_F=2}_{\text{Na}}, $ and $ \ket{\downarrow_{\text{Na}}} = \ket{F=1,m_F=1}_{\text{Na}}$. Among the stable spin combinations, $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}}$ and $\ket{\downarrow_{\text{Na}}\downarrow_{\text{Cs}}} $ both have small scattering lengths of $ 30.4a_0 $, and $ 13.7a_0 $ respectively, but the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}} $ combination has a large and negative scattering length of $ a(\uparrow_{\text{Na}} \downarrow_{\text{Cs}}) = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}. In addition to the increased atomic coupling, $ \Omega_a $, with the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination, coupled channel calculations show that the most weakly bound molecular state that is predominantly in this spin combination also has reduced coupling, $ \Omega_m $, with the excited state when compared with the $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}}$ and $\ket{\downarrow_{\text{Na}}\downarrow_{\text{Cs}}} $ bound states. Therefore, using an initial $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003 with the other combinations.

@@

Thus, we choose the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ spin combination as our initial state and drive to the first bound state for the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ spin combination. %(We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)

@@

%% Preparation
To perform the Raman transfer, we use our apparatus described in our previous work~\cite{Liu2019}. Our experiment begins by stochastically loading a single ${}^{23}\mathrm{Na}$ atom and a single ${}^{133}\mathrm{Cs}$ atom into an optical tweezer from a dual-species MOT\todo{cite na loading paper} into separate optical tweezers. The atoms are initially imaged to distinguish between loading of two atoms, one atom (Na or Cs), or no atom in order to perform post selection. We then perform simultaneous Raman sideband cooling (RSC) to cool both atoms into the 3-dimensional motional ground state of their optical tweezers. After RSC, the Na tweezer is moved by sweeping the frequency on an acoustical optical beam deflector (AOBD) to overlap with the Cs tweezer before smoothly ramping off, so that the Na and Cs atoms are merged into the same tweezer~\cite{Liu2019}. The spin states for the Na and Cs atoms after RSC and during the merge process are $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}} $. This states combination has a low scattering length, which allows the two atoms to be merged into the same tweezer with minimum pertubation on each other and thus they remain in the motional ground state after the merge.

After preparing the Na and Cs atoms in the same tweezer in a single quantum state, we need to drive the atoms into the large scattering length $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination. To do this, we perform a spin flip taking into account the interaction shift~\cite{Hood2019} using a Cs Raman transition to drive the Cs atom into the $\ket{\downarrow_{\text{Cs}}}$ state. The new spin state combination has a larger scattering length of $-693.8 a_0$ which generates a interaction shift of $-30.7 kHz$ in the tweezer. This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motion ground state.

% The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..

%% Transfer scheme
After the atoms are prepared in the $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}} $ hyperfine combination, we then perform the Raman transfer. The pulse sequence for this step is shown in Fig.~\ref{f-raman}B. Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal. In particular, we turn on two co-propagating frequencies in the tweezer during the Raman pulse. The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition, and also allows us to maximize the Raman Rabi frequency and minimize the transfer time. After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simultaneously ramping up the power of a different frequency so that the total tweezer power remains unchanged. Both frequencies are kept on for a variable length of time before the process is reversed and we return to having a single frequency in the tweezer.
In addition to reducing the number of laser beams during the Raman transition,
we also found the spectral purity of the laser to be critical for achieving a higher
transfer efficiency. The tweezer and Raman beams are generated by amplifying a $1037 \mathrm{nm}$
external cavity diode laser (ECDL) with a fiber amplifier,
which produces a broad band amplified spontaneous emission (ASE)
in addition to the desired frequency. This increases the scattering rate due to coupling to
other excited states.
We use a Bragg grating with a line width (FWHM) of $50 \mathrm{GHz}$ to clean up the
laser spectrum and found it reduces the scattering rate by at least a factor of $2$
for a particular single photon detuning.

@@

>>>>

\begin{abstract}
  We report on coherent association of a single weakly-bound NaCs molecule in an optical tweezer
  through an optical Raman transition without the use of a Feshbach resonance. Our scheme borrows transition dipole moment while reducing photon scattering by selecting a deeply bound electronic excited intermediate state.
  Starting from two atoms in their relative motional ground state,
  we achieve optical transfer efficiency of $69\%$.
  The molecule has a binding energy of $770.200516(24) \mathrm{MHz}$ at $8.8~\mathrm{G}$
  and lifetime up to $1 \mathrm{ms}$ \textcolor{blue}{(1~ms seems long here)} with more than $60\%$ of the molecule created in the
  motional ground state.
  This technique is general without relying on narrow excited state lines or Feshbach resonances and could allow a wider range of molecular species to be assembled atom-by-atom.
\end{abstract}

@@

Diverse species of fully quantum controlled  ultracold molecules are desired for a  wide variety of applications including precision measurements~\cite{Kondov2019,Nick_and_Ivan2017, PhysRevA.101.042504, Andreev2018, PhysRevLett.119.153001, hudson2011}, quantum simulations~\cite{Yao2018}, quantum  information processing~\cite{DeMille2002, Ni2018}, and studies of ultracold chemistry~\cite{Bohn2017,Bala2016,Hu1111}.
While many innovative approaches demonstrated in the last few years have directly cooled different species of diatomic or polyatomic molecules below 1~mK~\cite{Norrgard2016, Mitra1366}, the coldest and the highest phase-space-density gas to date in an ensemble~\cite{Demarco2018} or as individuals~\cite{Zhang2020}  have been achieved through the association of ultracold atoms.
% (any place to cite  molecular ion work?)
% Citations are not complete. Add them as you see fit.

Such ultracold molecular association takes advantage of the much developed cooling and trapping techniques for atoms as a starting point. To overcome the challenges of small wavefunction overlap and the large release of binding energy of converting atoms to deeply-bound molecules, a  two-step approach has been established to first associate atom pairs into weakly-bound molecules, and then transfer the molecules from this single internal state to a desired rovibrational and electronic state~\cite{Danzl2008, Ni2008,Lang2008, Takekoshi2014, Molony2014, Park2015, Guo2016, Kondov2019, Voges2020}.
So far, all of such association processes utilized a magnetic Feshbach scattering resonance and have been applied to bialkali molecules. The only exceptions are Sr$_2$ where narrow linewidth excited states are available and optical association can be driven coherently~\cite{Reinaudi2012,Stellmer2012} and $^{87}$Rb$^{85}$Rb where weakly bound molecules of a binding energy of a couple MHz exists~\cite{He331}. These requirements greatly limit the generality of previous association techniques.
%The requirement of a Feshbach resonance or a MHz-level binding energy bound state to enhance atom-to-molecule wavefunction overlap or the existence of narrow excited state lines limits the generality of previous association techniques. % to more diverse species.

Here, we demonstrate coherent association of an atom pair to a weakly bound molecule using a two-photon optical Raman transfer via an electronic excited state, schematically shown in Fig.~\ref{f-theory}A, neither using a Feshbach resonance, few MHz-level bound states, nor a narrow excited state. The resulting single molecule is in a single internal quantum state and predominately in its motional ground state.  Our scheme is based on a choice of vibrational state of the electronic excited state $c^3\Sigma^+(\Omega = 1)$ that has the theoretical best raman Rabi frequency to photon scattering ratio. To further increase this ratio and reduce technical requirements such as intensity stability, we choose an initial and final state where the matrix elements with the excited state are as balanced as possible. This approach minimizes the reliance on system specific properties and could therefore be applied to creating other molecular species or larger molecules atom-by-atom with full quantum state control.
% (also this result represents full quantum-state control of single [neutral] molecules, the second time ever (first being our NaCs Feshbach molecules))

@@

\textcolor{blue}{(need to make consistent concise terminology, excited state molecule, weakly bound molecule, molecular state, etc.  call them  state 1, 2, 3? or revert back to call the intermediate state without mentioning molecule?).} The essence of an optical Raman transfer can be illustrated using a three-level system (Fig.~\ref{f-theory}A), where the initial atomic state, the target weakly-bound molecular state are coupled to an intermediate state by two photons, $\Omega_a$ and $\Omega_m$, with one-photon detuning $ \Delta $, and two-photon detuning, $ \delta$.  %(Ultimately, we calculate with contribution of all vibrational states of the excited electronic potential, $c^3\Sigma^+$)
The transfer Raman Rabi Rate, $ \Omega_a\Omega_m / 2\Delta$, is accompanied by a photon scattering rate that is a sum of all coupling sources%, 
%$\Gamma_e \Omega^2 / 4\Delta^2 $, where $ \Gamma_e $ is the excited state linewidth
~\cite{Wineland2003}. 
Unlike for Raman transitions in atoms, the two coupling matrix elements here are greatly imbalanced %. Since $ \Omega_m $ is generally much larger than $ \Omega_a $
due to the small wavefunction overlap between the atomic state and the intermediate state, %the atomic state and the excited molecular state,
and therefore the scattering is predominantly from the molecular state. Furthermore, the energy difference between the atomic state and target molecular state is small ($ < 1~\mathrm{GHz} $) compared to the single photon detuning, $ \Delta $, so the molecular state can scatter off both beams roughly equally. Thus, the scattering is given by $ \Gamma_e \Omega_m^2 / 2\Delta^2$, where $ \Gamma_e $ is the excited state linewidth \footnote{We choose the two beams to have equal power, which gives the highest Raman Rabi Rate at a fixed total power. Thus, this results in a simple factor of 2 coming from scattering off 2 beams.}.
The ratio between the Raman Rabi frequency and the scattering rate is therefore $ \Omega_a/\Omega_m \times \Delta/\Gamma_e $. %, depends on the ratio of the two matrix elements and how far detuned the laser is from the transition in units of the linewidth. 
To ensure a coherent process, a detuning as large as possible, while maintaining a realistic Raman Rabi frequency, is preferred. %However, the detuning cannot be too large, since that will reduce the Raman Rabi frequency.
With the multiple excited vibrational states present in a molecular potential as intermediate states, the total scattering rate and Raman Rabi rate become a sum over the scattering rates and Raman Rabi rates of the individual intermediate states. Furthermore, for a more complete calculation, we also need to account for the effects of the excited atomic continuum, which is particularly important for the target molecular state.
\footnote{The sum of the squares of the wavefunction overlap between the weakly bound molecular state and all the excited intermediate states considered is only about 2\%, suggesting that there is significant matrix element between this weakly bound state and the excited atomic continuum. See supplementary information.} \textcolor{red}{(KW: I included a footnote here, but we can also consider putting this information into the main text?)}

Pioneering experiments used weakly-bound excited states as the intermediate state in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}. However, such choice of state suffers from strong scattering of the nearby excited atomic continuum to render it incoherent, resulting in molecule loss. This scattering is  proportional to $1/\delta_{thresh}^2$, where $\delta_{thresh}$ is the detuning from the dissociation threshold, and thus can  be made smaller by detuning away from the dissociation threshold.

@@

To find the optimal intermediate state, we perform a  calculation of the Raman Rabi frequency and scattering rate at different detunings from the atomic threshold taking into account of all states of the $c^3\Sigma^+(\Omega = 1)$ excited molecular state potential~\cite{Grochola2011} and the continuum~\cite{Liu2017}. 
As shown in Fig.~\ref{f-theory}B (full result in SM), the ratio of the Raman Rabi rate to scattering rate can be made larger for more deeply bound states compared to weakly bound states at a cost of a smaller Raman Rabi frequency.  
As a result, we choose %a deeply bound molecular excited state
the $v'=0$ of $c^3\Sigma^+(\Omega = 1)$ as an intermediate state to drive the Raman transition. %(mention the trend, also v'=12 will work as similarly as v'=0)

@@

In addition to the intermediate state, choosing an initial and a final state for a large  $ \Omega_a/\Omega_m $ ratio would allow large Raman Rabi coupling at a given detuning. Furthermore, a larger ratio also relaxes the intensity stability requirement, because this is also the ratio between the Raman Rabi coupling and the AC Stark shift of the molecular state, $ \Omega_m^2 / 2\Delta $ \footnote{There is an additional factor of 2, with both beams at equal power, to account for the Stark shift caused by both beams.}.
%and relax the intensity stability requirement due to the AC Stark shift of the molecular state, $ \Omega_m^2 / 2\Delta $ \footnote{There is an additional factor of 2 to account for the Stark shift caused by both beams.} 
%As previously discussed, the ratio of the Raman Rabi rate to the scattering rate is proportional to the $ \Omega_a/\Omega_m $ ratio. The smaller this ratio is, the farther the laser needs to be detuned to achieve the same Raman Rabi rate to scattering rate ratio, which lowers the Raman Rabi rate. In addition to reducing how far the laser needs to be detuned from the transition, a larger $ \Omega_a/\Omega_m$ ratio also relaxes the intensity stability requirement, a key potential technical limitation. The position of the two photon resonance depends on the laser power predominantly through the AC Stark shift on the molecular state, $ \Omega_m^2 / 2\Delta $ \footnote{There is an additional factor of 2 to account for the Stark shift caused by both beams.}. The ratio of the AC Stark shift to the Raman Rabi frequency is $ \Omega_m / \Omega_a $, Thus, the laser intensity needs to be stabilized to better than the inverse of this ratio to fluctuate by less than a linewidth in a coherent process. The ratio, $ \Omega_a/\Omega_m $ can be changed through the choice of initial and final states. 
%Because of the large atom and molecule wavefunction mismatch, choosing an initial atomic state that has more amplitude at smaller internuclear distance can increase the coupling $\Omega_a$. \textcolor{blue}{(the two sentences have the same idea.)}
%it can be made larger by increasing the coupling of the atomic state with the excited molecular state. 
Due to the small size of the intermediate state wavefunction, the coupling $\Omega_a$ is approximately proportional to the value of the relative atomic wavefunction at short distance within the molecular potential. To increase the amplitude within the molecular potential, one can increase the external confinement of atom pairs. Using a harmonic oscillator approximation, the short range amplitude is proportional to $ \omega_{\text{trap}}^{3/8} $, where $ \omega_{\text{trap}} $ is the trap frequency. Alternatively, one can choose an atomic pair state with a large scattering length (positive or negative).
For these states, the phase shift in the relative wavefunction between the atoms can significantly increase the short range wavefunction (Fig.~\ref{f-theory}C). %The increase in the coupling is proportional to (quote/cite Olive's equation?). 
For our system of Na and Cs atoms, we chose  a  spin state combination $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}\equiv \ket{F=2,m_F=2}_{\text{Na}}\ket{F=3,m_F=3}_{\text{Cs}} $that has a large and negative scattering length of $ a(\uparrow_{\text{Na}} \downarrow_{\text{Cs}}) = -693.8a_0$~\cite{Hood2019}. We note that other stable spin combinations give smaller scattering lengths ($<~50~a_0$) \textcolor{blue}{(define arbitrarily).} 
%We denote the possible hyperfine states of the atoms as $ \ket{\uparrow_{\text{Cs}}} = \ket{F=4,m_F=4}_{\text{Cs}}, \ket{\downarrow_{\text{Cs}}} = \ket{F=3,m_F=3}_{\text{Cs}}, \ket{\uparrow_{\text{Na}}} = \ket{F=2,m_F=2}_{\text{Na}}, $ and $ \ket{\downarrow_{\text{Na}}} = \ket{F=1,m_F=1}_{\text{Na}}$. Among the stable spin combinations, $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}}$ and $\ket{\downarrow_{\text{Na}}\downarrow_{\text{Cs}}} $ both have small scattering lengths of $ 30.4a_0 $, and $ 13.7a_0 $ respectively, but the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}} $ combination has a large and negative scattering length of $ a(\uparrow_{\text{Na}} \downarrow_{\text{Cs}}) = -693.8a_0 $ (interaction shift $\approx$ binding?)~\cite{Hood2019}. 
In addition to the increased atomic coupling, $ \Omega_a $, %with the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination, 
coupled channel calculations show that the target molecular state that is predominantly in this spin combination also has reduced coupling, $ \Omega_m $, with the intermediate state when compared to bound states of the other stable spin combinations % $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}}$ and $\ket{\downarrow_{\text{Na}}\downarrow_{\text{Cs}}} $ bound states. 
Therefore, using an initial $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination results in a $ \Omega_a/\Omega_m$ ratio of about 0.05 instead of a ratio of about 0.003 with the other combinations, and thus only an required intensity stability of 5\% instead of 0.3\%.

@@

%Thus, we choose the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ spin combination as our initial state and drive to the first bound state for the $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ spin combination. 
\textcolor{blue}{(clean up the paragraph some more).} %(We might want to mention that those ratios are for 80 kHz spherical trap if we want to give more details about the coupled channel calculation anywhere...)

@@

%% Preparation
Experimentally, we first prepare two atoms in a well-defined external and internal quantum state using techniques developed previously~\cite{Liu2018, Liu2019, Wang2019}. In brief, the experimental cycle begins by  loading a single ${}^{23}\mathrm{Na}$ atom and a single ${}^{133}\mathrm{Cs}$ atom stochastically into separate optical tweezers. The atoms are initially imaged to distinguish between loading of two atoms, one atom (Na or Cs), or no atom, which is compared to the image at the end of the experiment. Raman sideband cooling is then applied to cool both atoms simultaneous into the 3-dimensional motional ground state of their optical tweezers. After cooling, the Na and Cs atoms are in a spin state of $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}}\equiv \ket{F=2,m_F=2}_{\text{Na}}\ket{F=4,m_F=4}_{\text{Cs}} $ %and are merged into the same tweezer~\cite{Liu2019}. %The spin states for the Na and Cs atoms after RSC and during the merge process are $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}} $. 
that has a low scattering length. The small two atom interaction allows the two atoms to be merged into the same tweezer with minimum pertubation  and remain in the motional ground state after the merge.

%After preparing the Na and Cs atoms in the same tweezer in a single quantum state, 
Next, we  drive the atoms into the large scattering length $\ket{\uparrow_{\text{Na}} \downarrow_{\text{Cs}}}$ hyperfine combination as the initial atomic state of Raman transfer by performing a Cs spin flip while taking into account the $-30.7 kHz$ interaction shift~\cite{Hood2019}.  %using a Cs Raman transition to drive the Cs atom into the $\ket{\downarrow_{\text{Cs}}}$ state. The new spin state combination has a larger scattering length of $-693.8 a_0$ which generates a interaction shift of $-30.7 kHz$ in the tweezer. 
This spin flip selectively transfers atoms in the relative motion ground state \footnote{This interaction shift is larger than the differential axial trapping frequency between Na and Cs atoms, which decouples the relative and center of mass motional state and improves the robustness of our preparation of the relative motion ground state.}, and for the experiment reported here, this is 31\% of the initial population of two atoms loaded in separate optical tweezers.
% The stronger interaction in this spin state also enhances the atomic wavefunction at short range and increases its overlap with the intermediate molecular state used for our Raman transfer..

%% Transfer scheme
%After the atoms are prepared in the $\ket{\uparrow_{\text{Na}}\uparrow_{\text{Cs}}} $ hyperfine combination, we then perform the Raman transfer. 
To perform Raman transfer of an atom pair to the targeted weakly-bound molecular state, we use the tweezer itself as the Raman beams by turning on two co-propagating frequencies in the tweezer during the Raman pulse (Fig.~\ref{f-raman}A). The dual use of the tweezer beam not only eliminates additional scattering sources or undesired laser frequencies, but also allows a tight focus to  maximize the Raman Rabi frequency and minimize the transfer time. %to allow perfect overlap and to eliminate additional beams and therefore scattering sources. 
The pulse sequence is shown in Fig.~\ref{f-raman}B. %Instead of adding another beam to drive the Raman transition on the atoms in the tweezer, we use the tweezer itself to achieve this goal. 
%In particular, we turn on two co-propagating frequencies in the tweezer during the Raman pulse. The dual use of the tweezer beam ensures that there is not any undesired laser frequency that can interfere with the Raman transition, and also allows us to maximize the Raman Rabi frequency and minimize the transfer time. 
After the total tweezer power is set to the desired value, we smoothly ramp down the power of one frequency in the tweezer while simultaneously ramping up the power of a different frequency so that the total tweezer power remains unchanged. Both frequencies are kept on for a specified duration before the process is reversed and the tweezer returns to a single frequency.
%In addition to reducing the number of laser beams during the Raman transition, 
Furthermore, we use a Bragg grating with a line width (FWHM) of $50 \mathrm{GHz}$ to filter  the laser spectrum generated by a fiber amplifier that is seeded with a $1037~\mathrm{nm}$ external cavity diode laser. We observed a reduction of the scattering rate by at least  a factor of $2$ \textcolor{blue}{(can we be more definite?)}
(for a particular single photon detuning) due to the (xx dB?) suppression   of the broadband amplified spontaneous emission (ASE) from the laser that   couples to other excited states.

%found the spectral purity of the laser for Raman beams to be critical for achieving a higher transfer efficiency. 
%The tweezer/Raman beams are generated by a fiber amplifier seeded with a $1037 \mathrm{nm}$ external cavity diode laser. 
%by amplifying a $1037 \mathrm{nm}$ external cavity diode laser (ECDL) with a fiber amplifier,
%The diode laser produces the desired frequency on top of a broad band amplified spontaneous emission (ASE).  We use a Bragg grating with a line width (FWHM) of $50 \mathrm{GHz}$ to clean up the laser spectrum and found it reduces the scattering rate by at least a factor of $2$
%for a particular single photon detuning.

%in addition to the desired frequency. This increases the scattering rate due to coupling to other excited states.

\begin{figure*}[t!]
  \includegraphics[height=4.5cm]{fig3.pdf}
  \caption{
    (A) Fitting of Raman detuning scans at different times to a model of Raman transition
    with loss on the atom and molecule state. The combined fit is used to determine
    both the Raman Rabi frequency and the loss rates.
    (B) \todo{inset?} Two-body atom lifetime in $15 \mathrm{mW}$ of trap depth caused by
    off-resonance photoassociation.
    This is used to improve the fitting of the Raman transfer data.
    (C) Direct measurement of molecule lifetime in $15 \mathrm{mW}$ of trap depth.
    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
    The lifetime is consistent with the $0.204(13) \mathrm{ms}$
    measured from the Raman transition data.
    The oscillation in the survival is the result of the interference
    between the two Raman pulses with incomplete transfer.
    \label{f-lifetime}}
\end{figure*}

@@

\begin{acknowledgments}
We would like to thank Bo Gao and Paul Julienne, Rosario (?) (anybody else) for discussion. This work is supported by the NSF~(PHY-1806595), the AFOSR~(FA9550-19-1-0089), ARO DURIP (W911NF1810194) and the Arnold and Mabel Beckman foundation. J.~T.~Z. is supported by a National Defense Science and Engineering Graduate Fellowship. W.~C. is supported by a Max Planck-Harvard Research Center for Quantum Optics fellowship. K.~W. is supported by an NSF GRFP fellowship. J.~M.~H. is supported by the U.K. Engineering and Physical Sciences Research Council (EPSRC) Grants No.\ EP/N007085/1, EP/P008275/1 and EP/P01058X/1.
\end{acknowledgments}
